---
title: "SQuaScheD -- Additional Material"
author: "Julien Gaugaz"
output:
  knitrBootstrap::bootstrap_document:
    title: "SQuaScheD -- Additional Material"
    theme: spacelab
    highlight: sunburst
  html_document:
    theme: spacelab
  md_document:
    variant: markdown_github
    toc: true
    toc_depth: 2
---

We present here additional material related to the paper "Here is the Data. Where is its Schema?" submitted to WSDM'15.

```{r include = FALSE}
library(knitr)
library(clusterSim)
opts_chunk$set(eval = T,
               cache = T,
               autodep = T,
               fig.width = 10, 
               fig.height = 6, 
               results = 'asis',
               warning = F,
               message = F,
               error = F,
               echo = F)
wd <- function() setwd("../schemdesc/r")
wd()
source("R/hgraph.R")
source("R/dataset_hierarchies.R")
source("R/eigs.R")
source("R/inextrinsic.R")
source("R/results-utils.R")
source("R/evaluation.R")
source("R/paper_graph-utils.R")
library(igraph)
library(ggplot2)
library(reshape2)
library(tidyr)
library(dplyr, warn.conflicts=F)
library(pander, warn.conflicts=F)
panderOptions("table.style", "rmarkdown")
panderOptions("table.split.table", Inf)
library(data.table, warn.conflicts=F)
library(magrittr)
library(gridExtra)
library(xtable)
library(scales)
library(jsonlite)
```

# MDL Evolution in SQuaScheD
The figures below show the evolution of the MDL, class-precision, -recall, and -F2 along the steps of the SQUASCHED process for all datasets.
```{r fig.height = 10, fig.width=20}
wd()
results <- load.results() %>%
  friendly.names %>% 
  filter(builder == "spectral", dataset != "sample") %>%
  arrange(dataset)
for(row in  1:nrow(results)){
  res <- results[row,]
  pandoc.header(res$dataset.fullName, level = 2)
    capture.output(read.inext(res, rm.lowerCotopy.weights=F) %>% 
                     plot.inext(main=res$dataset, ggtheme=theme_ppr, beta=2) %>%
                     print, file = "/dev/null")
}
```

# Ground Truth Class Distribution
Distribution of the bottom-most ground-truth class in the discovered class hierarchy for all datasets.

```{r}
wd()
results <- load.results() %>%
  friendly.names %>% 
  filter.selected %>%
  filter.spectral %>%
  mutate(algo.name = algo %>% 
           as.character %>%
           gsub("spectral", "SQuaScheD", .) %>% 
           gsub("ent-cobweb-", "COBWEB ", .))
datasets <- results %>% with(dataset.fullName) %>% unique %>% sort 
algo.names <- results %>% with(algo.name) %>% unique %>% sort(decreasing = T)
plot.hierarchy.tree <- function(ds, alg) tryCatch({
  pandoc.header(alg, level=3)
  if(alg == "Ground Truth") {
    res <- results %>% filter(dataset.fullName == ds, algo == "spectral")
    hierarchy.for.dataset(res$dataset) %>% graph.gt.h(rescale=T) %>% plot.tree(rescale=F, vertex.size=11, vertex.label.dist=-.8, main = paste("Ground Truth", res$dataset, sep = " - "))
  } else {
    res <- results %>% filter(dataset.fullName == ds, algo.name == alg)
    is.pruned <- !(res$algo == "spectral") && (res %>% with(pruned)) != "not-pruned"
    is.partitioned <- !(res$algo == "spectral") && (res %>% with(assignment)) == "partitioning"
    g <- graph.h(res, rescale=T, set.vertices=set.precision.pie.vertices, aspect.ratio = 4, partitioning = is.partitioned, pruned = is.pruned) 
    capture.output(plot.tree(g, rescale=F, vertex.label=NA, vertex.size=11) %>% print, file = "/dev/null")
  }
})
```

```{r fig.height=25, fig.width=50}
wd()
ds <- datasets[1]
pandoc.header(ds, level=2)
plot.hierarchy.tree(ds, "Ground Truth")
for(alg in algo.names) {
  plot.hierarchy.tree(ds, alg)
}
```

```{r fig.height=25, fig.width=50, eval=TRUE}
wd()
ds <- datasets[2]
pandoc.header(ds, level=2)
plot.hierarchy.tree(ds, "Ground Truth")
for(alg in algo.names) {
  plot.hierarchy.tree(ds, alg)
}
```

```{r fig.height=25, fig.width=50, eval=TRUE}
wd()
ds <- datasets[3]
pandoc.header(ds, level=2)
plot.hierarchy.tree(ds, "Ground Truth")
for(alg in algo.names) {
  plot.hierarchy.tree(ds, alg)
}
```

```{r fig.height=25, fig.width=50, eval=TRUE}
wd()
ds <- datasets[4]
pandoc.header(ds, level=2)
plot.hierarchy.tree(ds, "Ground Truth")
for(alg in algo.names) {
  plot.hierarchy.tree(ds, alg)
}
```

```{r fig.height=25, fig.width=50, eval=TRUE}
wd()
ds <- datasets[5]
pandoc.header(ds, level=2)
plot.hierarchy.tree(ds, "Ground Truth")
for(alg in algo.names) {
  plot.hierarchy.tree(ds, alg)
}
```

```{r fig.height=25, fig.width=50}
wd()
ds <- datasets[6]
pandoc.header(ds, level=2)
plot.hierarchy.tree(ds, "Ground Truth")
for(alg in algo.names) {
  plot.hierarchy.tree(ds, alg)
}
```

```{r fig.height=25, fig.width=50}
wd()
ds <- datasets[7]
pandoc.header(ds, level=2)
plot.hierarchy.tree(ds, "Ground Truth")
for(alg in algo.names) {
  plot.hierarchy.tree(ds, alg)
}
```

```{r fig.height=25, fig.width=50}
wd()
ds <- datasets[8]
pandoc.header(ds, level=2)
plot.hierarchy.tree(ds, "Ground Truth")
for(alg in algo.names) {
  plot.hierarchy.tree(ds, alg)
}
```



